How to Analyze Build Logs\\ ---\\ A~Comparative Study of Chunk~Retrieval~Techniques

### 2020-03-09 tse-paper/content.tex
try to concept new introduction, more heading fixes

Continuous Integration (CI) has become a common practice in software
engineering~\cite{hilton2016usage}.  Many software projects use
CI~\cite{hilton2016usage,staahl2014modeling,beller2017oops} to detect
bugs early~\cite{vasilescu2015quality,duvall2007continuous}, improve
developer productivity~\cite{miller2008hundred,hilton2016usage} and
communication~\cite{downs2012ambient}.  CI builds produce logs which
report results of various sub-steps within the build.  These build logs
contain a lot of valuable information for developers and researchers---for
example, descriptions of compile errors, linter warnings or failed
tests~\cite{beller2017oops,seo2014programmers,vassallo2017a-tale}.

\textbf{Motivation.} The information stored in build logs can and has
already been used for a variety of applications. One prominent dataset
in the space, TravisTorrent, was featured as the MSR Data Challenge
2017~\cite{msr17challenge}. To date, scientist and practitioners alike
have used it and other, proprietary datasets to understand and
cateogrize Continuous Integration build
failures~\cite{islam2017insights}, to do research on testing
practices~\cite{orellana2017differences}, to train classifiers to
predict the build outcome and
duration~\cite{ni2017cost,bisong2017built,machalica2019predictive},
and to investigate static analysis tools in CI
builds~\cite{zampetti2017open}. Therefore, being able to efficiently
and correctly extract information from build logs is paramount to the
future of a variety of fields depending on it.

@@

The goal of this thesis is to investigate different chunk retrieval techniques for build logs and describe under which circumstances certain techniques can be recommended over others.
We aim to characterize different chunk retrieval techniques, as well as the information retrievable from CI build logs.
For \textbf{Research Question 1} (\textbf{RQ1}), we analyze which criteria influence the suitability of a chunk retrieval technique for CI build logs.

@@

\paragraph{Our work contributes:}
\begin{itemize}
  \item A tool unifying several chunk retrieval techniques namely:
        \begin{itemize}
          \item program synthesis from examples using the Microsoft PROSE library (PBE),
          \item a common information retrieval approach using text similarity (CTS), and
          \item a keyword search approach (KWS).
        \end{itemize}
  \item A validated data set of about 800 logs from failed Travis CI builds manually-labelled with:
        \begin{itemize}
          \item the substring of the log describing the reason the build failed,
          \item keywords we would use to search for these substrings, and
          \item a categorization of the substrings according to their structural representation within the build log.
        \end{itemize}
  \item Recommendations for the configuration of each of the investigated chunk retrieval techniques.
  \item Guidelines on choosing a suitable chunk retrieval technique.
\end{itemize}

@@

\section{Related Work}
\begin{itemize}
	\item CI research? could show how researchers could use chunk retrieval for existing studies (then I would only mention studies that do build log analysis)
	\item build log augmentation (BART paper, ICSE Amar et al.)
	\item ``foundational techniques'', e.g. explaining how PROSE synthesis algorithm works, I would move to the explanation of the method
\end{itemize}

\label{sec:rw}
This chapter presents various research works adjacent or foundational to our work.
The first section presents existing work in the field of continuous integration (CI) and showcases how researchers analyze build logs.
In the second section we describe the existing methods which are the foundation for the chunk retrieval techniques we investigate.

\subsection{Continuous Integration and Build Logs}
We describe existing studies about CI to show that CI is a relevant topic within the software engineering research community.
We explain how researchers gather information about CI usage in software projects through build log analysis and why the chunk retrieval techniques we investigate simplifies their data collection.
This section moves on to past works about augmenting build logs to make it easier for developers to inspect them.
The presented approaches are related to and can benefit from the techniques we analyze in this thesis.
Further, we classify build logs as semi-structured data and differentiate our work from system log analysis.

\subsubsection{Build Failures in CI}
Various researchers look into why CI builds fail and into the impact of build failures on the development workflow.
Seo et al.~\cite{seo2014programmers} find that a small group of error types such as dependency mismatches are the most prominent cause of build failures at Google.
In addition, they notice that most failures are resolved within two builds.
Rausch et al.~\cite{rausch2017empirical} analyze CI builds of open source Java projects and find that most builds fail because of failing tests.
For most projects, over half of the failed builds follow a previous failed build.
Rausch et al.'s data shows that most failures occur in the second half of the build runtime, which can cause long delays in the feedback loop, especially when builds are automatically retried upon failure.
Vassallo et al.~\cite{vassallo2017a-tale} compare open source projects in Java to industrial ones.
They determine that testing failures are more common than compilation errors.
Open source builds fail most often because of unit tests, whereas release preparations are the primary cause in industrial projects.

\subsubsection{Supporting Log Analysis with Chunk Retrieval}
To leverage the valuable information within build logs the researchers presented in this section build parsers and regular expression-based programs.
This task of retrieving specific chunks of text from the build logs can be solved by the chunk retrieval techniques we compare in this thesis.
Our results can support researchers in choosing a suitable technique for their data set of build logs and the chunks they want to retrieve.
By relieving them from building custom parsers we enable them to cover a much wider range of languages and build tools in their studies.

\subsection{Augmentation of Build Logs}
\label{sec:rw-bl-analysis}
Build logs are a valuable data source for developers to find out why their build failed.
Several researchers are looking into supporting developers to process the verbose build logs.
Vassallo et al.~\cite{vassallo2018un-break} try to shorten the time it takes developers to understand build logs.
They parse Maven~\cite{maven2019website} build logs into a structured representation and create hint generators.
The hint generators leverage this structured access to the information within the build log to propose fixes.
For example, one of the hint generators queries stack overflow for discussions related to why the build failed.
In a qualitative study they observed that highlighting the locality and context of an issue is helpful to programmers.
Their tool BART is published as a Jenkins Plugin~\cite{bart2019plugin}.
The chunk retrieval techniques we compare in this thesis can be used to fill similar structured representations with information from build logs.
As they simplify the construction of parsers they would enable developers and researchers to cover a wider array of build tools, which is the main influence factor on the structure of a build log.

@@

Abiteboul proposes an approach to overlay the semi-structured data with a structured layer.
The additional layer can answer queries and give access to the semi-structured data relevant to a query.
In contrast to that, this thesis takes a look at techniques to gather a specific, pre-specified information without the need to parse, understand or estimate the whole structure of a log.

@@

Classic log parsers interpret the whole log file into a sequence of events.
A similar approach could also be applied to build logs to determine the sequence of executed build steps or phases.
In this thesis we take a different approach and focus on extracting a single specified information from the build log as a whole with chunk retrieval techniques.
Chunk retrieval techniques are used as a part of log parsing to retrieve the values of variable parts in a log message, e.g.\ by using regular expressions~\cite{nagappan2010abstracting,xu2009detecting}.

@@

\section{Chunk Retrieval Techniques}
\label{sec:techniques}
This chapter introduces the concept of chunk retrieval techniques.
We use these techniques to extract text chunks from build logs that represent a specific, targeted information.
This chapter first presents how a build log, which we take as input to the chunk retrieval, is created by a continuous integration (CI) build.
Next, the chapter describes retrievable information chunks in build logs and gives examples found in Travis CI build logs.
We illustrate why it is useful to extract the presented information chunks.
The following section introduces our concept of chunk retrieval techniques.
We present the three chunk retrieval techniques we investigate in this thesis:
program synthesis by example (PBE), common text similarity (CTS) and keyword search (KWS).

@@

\subsection{Characteristics of Chunk Retrieval Techniques}
\label{sec:blirt}
For this thesis, we want to evaluate different techniques to retrieve information chunks from build logs, which we call \emph{chunk retrieval techniques}.
The techniques we investigate do not require to parse the structure of a whole build log, but focus on extracting just one specific information.

@@

\todo{move implementation here?}

@@

\paragraph{Configuration and Input}
Our study results show that chunk retrieval with PBE gives best results when the training examples are from one structural category.
This means it is suited to retrieve information chunks that always have the same surrounding structure.
To extract for example the reason a build failed, the log passage describing the failure would always have to be started and ended the same way.

@@

\paragraph{Retrieval Output Usage}
If the program synthesis succeeds and applying the regular expression program yields an output, PBE shows a high precision and a high recall.
The tool clearly identifies a failing program synthesis or when no output from the program applied to a build log is obtained.
Therefore, if there is an output, the user can have high confidence that it is the correct output.
This makes output from PBE chunk retrieval well suited for consumption by other software components.

\subsubsection{Common Text Similarity (CTS)}
\paragraph{Configuration and Input}
Chunk retrieval using CTS also yields better results the fewer structural categories are present in the training and test examples.

@@

\paragraph{Retrieval Output Usage}
CTS has good precision and recall on average, though the precision or recall of a chunk retrieval run is very hard to predict from the given result.
Therefore, retrieval output from CTS is suited to be read by a human.

\subsubsection{Keyword Search (KWS)}
\paragraph{Configuration and Input}
KWS has a higher recall than the two other techniques for multiple structural categories present in the training and test examples.
This makes KWS a good technique if there is little prior knowledge on how the targeted log chunk is represented in the build log to be analyzed.
For the example of extracting the reason the build failed, KWS is best suited if a build can fail in various steps logged by different tools and no pre-categorization of where the build failed is available.

@@

\paragraph{Retrieval Output Usage}
Even though KWS has the highest recall of all three techniques, its precision is also the lowest.
The output of a chunk retrieval with KWS is well suited to be read by humans.

@@

\emph{Caveat!} This is a preliminary theory based on the results from our comparison study.
The recommendations are therefore based on our implementation of the chunk retrieval techniques as well as the logs in the \emph{LogChunks} data set.

@@

\subsubsection{Example of Using the Recommendation Scheme}
To illustrate how one would use our decision tree to find a suitable chunk retrieval technique we describe two concrete examples: a researcher investigating why CI builds fail and a software team wanting to monitor their build performance.

@@

\subsection{Implementation}
Our results are highly dependent on our implementation of the investigated chunk retrieval techniques and the libraries we used.
Our implementation of PBE is severely based on the program synthesis provided by PROSE\@.
Its limitations are therefore also mainly influenced by this library.
For example, the need for examples from a single structural category stems from the fact that FlashExtract cannot learn regular expression programs with arbitrary boolean conjunctions and disjunctions~\cite{mayer2015user}.
This limitation was necessary to keep the synthesis performance reasonable.

@@

\subsection{Data Set}
The outcomes of our comparison study are highly dependent on the build logs from the \emph{LogChunks} data set.
It only consists of build logs from open source projects and therefore it is not clear whether our results are generalizable to industry projects.
We only collected build logs from Travis CI, however we chose to evaluate on an information chunk whose format is not dependent on Travis CI\@.
This is because the reason the build failed is described within the build logs by the tools themselves and not the Travis CI environment.

\subsection{Training Set Size}
Especially the results for CTS might be influenced by the fact that we only trained on one to five examples.
We chose this small training set size as the training examples have to be provided per repository and we expect a developer to not want to provide more examples than the small numbers we evaluated on.

\subsection{Few Samples with Many Structural Categories}
Our comparison study shows fewer measurements with many structural categories than with one category.
This stems from the fact that we use a realistic data set which in many cases has only one or few structural categories.

\section{Conclusion and Future Work}
\label{sec:conclusion-fw}
The goal of this thesis was to support researchers and developers in their decision on how to analyze build logs.
We implemented and compared three different chunk retrieval techniques on our data set \emph{LogChunks}, composed of 797 manually labeled build logs from a broad range of 80 repositories.
Our results show that the structural representation of the targeted information in the build logs is the main factor to consider when choosing a suitable technique.
Secondary factors are the desired confidence into recall and precision of the produced output and whether precision or recall is more important for the task at hand.

There are various future research opportunities based on our work:
\begin{itemize}
  \item \textbf{Further Analysis of \emph{LogChunks}} We created the \emph{LogChunks} data set specifically for our comparative study, though it can be the basis for various further analyses of build log data.
  The keywords, for example, can be investigated to answer which keywords are used to search for the reason the build failed within build logs.
  \item \textbf{Cross-Repository Build Log Analysis} We trained and tested each chunk retrieval technique on examples from the same repository.
  We propose to analyze how techniques could be trained across repositories, building the cornerstones for build environment-agnostic analysis tools.
  \item \textbf{Comparison with more Chunk Retrieval Techniques} This thesis investigates the three chunk retrieval techniques PBE, CTS and KWS\@.
  Our study design can be reused to evaluate other build log analysis techniques, such as the diff and information retrieval approach by Amar et al.~\cite{amar2019mining}.
  \item \textbf{Refinement of Retrieval Quality for each Technique} We investigated basic configurations of existing techniques applied to chunk retrieval from build logs.
  In a next step, each of these techniques could be refined to better approach the domain of build logs.
  The \emph{LogChunks} data set and our study results act as a baseline to benchmark such technique improvements.
  We propose the following improvements:
    \begin{itemize}
      \item \textbf{Custom Ranking and Tokens for PBE} The program synthesis through PROSE ranks possible programs according to what the user most likely intended.
      One could adapt the ranking rules provided by the FlashExtract DSL to fit common build log chunk retrieval tasks.
      FlashExtract includes special tokens when enumerating possible regular expressions.
      One could extend these with tokens found in build logs, such as ``-'',``='',``ERROR'' or ``[OK''.
      \item \textbf{Meta-Parameter Optimization for CTS} Information retrieval techniques have various meta-parameters which can be optimized for the specific use case~\cite{panichella2016parameterizing}.
      We propose to further investigate improvements in preprocessing of the log text, in tokenization of the log lines into terms and in stop words lists.
    \end{itemize}
  \item \textbf{Usability Analysis of Chunk Retrieval Output} Our analysis of the output produced by the chunk retrieval focuses on precision and recall.
  We propose to investigate how useful these outputs are to developers through controlled experiments.
\end{itemize}

>>>>

\textbf{Motivation.}
Continuous Integration (CI) has become a common practice in software
engineering~\cite{hilton2016usage}.  Many software projects use
CI~\cite{hilton2016usage,staahl2014modeling,beller2017oops} to detect
bugs early~\cite{vasilescu2015quality,duvall2007continuous}, improve
developer productivity~\cite{miller2008hundred,hilton2016usage} and
communication~\cite{downs2012ambient}.  CI builds produce logs which
report results of various sub-steps within the build.  These build logs
contain a lot of valuable information for developers and researchers---for
example, descriptions of compile errors, linter warnings or failed
tests~\cite{beller2017oops,seo2014programmers,vassallo2017a-tale}.

CI builds produce logs which report the results of the steps within the build. The information stored in build logs can and has
already been used for a variety of applications. One prominent dataset
in the space, TravisTorrent, was featured as the MSR Data Challenge
2017~\cite{msr17challenge}. To date, scientist and practitioners alike
have used it and other, proprietary datasets to understand and
cateogrize Continuous Integration build
failures~\cite{islam2017insights}, to do research on testing
practices~\cite{orellana2017differences}, to train classifiers to
predict the build outcome and
duration~\cite{ni2017cost,bisong2017built,machalica2019predictive},
and to investigate static analysis tools in CI
builds~\cite{zampetti2017open}. Therefore, being able to efficiently
and correctly extract information from build logs is paramount to the
future of a variety of fields depending on it.

@@

The goal of this paper is to investigate different chunk retrieval techniques for build logs and describe under which circumstances certain techniques can be recommended over others.
We aim to characterize different chunk retrieval techniques.
For \textbf{Research Question 1} (\textbf{RQ1}), we analyze which criteria influence the suitability of a chunk retrieval technique for CI build logs.

@@

\noindent
\textbf{Our work contributes:}
\begin{itemize}
  \item A tool unifying several chunk retrieval techniques namely:
        \begin{itemize}
          \item program synthesis from examples using the Microsoft PROSE library (PBE),
          \item a common information retrieval approach using text similarity (CTS), and
          \item a keyword search approach (KWS).
        \end{itemize}
  \item Recommendations for the configuration of each of the investigated chunk retrieval techniques.
  \item Guidelines on choosing a suitable chunk retrieval technique.
\end{itemize}

@@

\section{Related Work}
\label{sec:rw}
We explain how researchers gather information about CI usage in software projects through build log analysis and why the chunk retrieval techniques we investigate simplifies their data collection.
This section moves on to past works about augmenting build logs to make it easier for developers to inspect them.
The presented approaches are related to and can benefit from the techniques we analyze in this paper.
Further, we classify build logs as semi-structured data and differentiate our work from system log analysis.
% In this section we cover previous works on CI and how resarchers use the
% information within build logs to investigate software engineering processes and
% support developers.

\subsection{Build Failures in CI}
Various researchers look into why CI builds fail and into the impact of build failures on the development workflow.

Seo et al.~\cite{seo2014programmers} find that a small group of error types such as dependency mismatches are the most prominent cause of build failures at Google.
In addition, they notice that most failures are resolved within two builds.
They based their analyses on sets of build logs collected from industry partners.
They develop a custom parser to classify error messages reported by Java and C++ builds.

Rausch et al.~\cite{rausch2017empirical} analyze CI builds of open source Java projects and find that most builds fail because of failing tests.
For most projects, over half of the failed builds follow a previous failed build.
Rausch et al.'s data shows that most failures occur in the second half of the build runtime, which can cause long delays in the feedback loop, especially when builds are automatically retried upon failure.

Vassallo et al.~\cite{vassallo2017a-tale} compare open source projects in Java to industrial ones.
They determine that testing failures are more common than compilation errors.
Open source builds fail most often because of unit tests, whereas release preparations are the primary cause in industrial projects.
Their data stems from analyzing build logs from \emph{TravisTorrent}~\cite{beller2017travistorrent} with regular expressions.

Ghaleb et al.~\cite{ghaleb2019studying} aim to identify noise in build breakage data.
They classify build failures from \emph{TravisTorrent} according to whether they were caused by an environmental failure or caused by a developer change.
Their analysis starts with manual categorization of build logs.
They select keywords and strings that identify their targeted categories and code a script to automatically classify logs based on these keywords.

\noindent
\textbf{Supporting Log Analysis with Chunk Retrieval}
To leverage the valuable information within build logs the researchers presented in this section build parsers and regular expression-based programs.
This task of retrieving specific chunks of text from the build logs can be solved by the chunk retrieval techniques we compare in this paper.
Our results can support researchers in choosing a suitable technique for their data set of build logs and the chunks they want to retrieve.
By relieving them from building custom parsers we enable them to cover a much wider range of languages and build tools in their studies.

\subsection{Augmentation of Build Logs}
\label{sec:rw-bl-analysis}
Build logs are a valuable data source for developers to find out why their build failed.
Several researchers are looking into supporting developers to process the verbose build logs.
Vassallo et al.~\cite{vassallo2018un-break} try to shorten the time it takes developers to understand build logs.
They parse Maven~\cite{maven2019website} build logs into a structured representation and create hint generators.
The hint generators leverage this structured access to the information within the build log to propose fixes.
For example, one of the hint generators queries stack overflow for discussions related to why the build failed.
In a qualitative study they observed that highlighting the locality and context of an issue is helpful to programmers.
Their tool BART is published as a Jenkins Plugin~\cite{bart2019plugin}.
The chunk retrieval techniques we compare in this paper can be used to fill similar structured representations with information from build logs.
As they simplify the construction of parsers they would enable developers and researchers to cover a wider array of build tools, which is the main influence factor on the structure of a build log.

@@

Abiteboul proposes an approach to overlay the semi-structured data with a structured layer.
The additional layer can answer queries and give access to the semi-structured data relevant to a query.
In contrast to that, this paper takes a look at techniques to gather a specific, pre-specified information without the need to parse, understand or estimate the whole structure of a log.

@@

Classic log parsers interpret the whole log file into a sequence of events.
A similar approach could also be applied to build logs to determine the sequence of executed build steps or phases.
In this paper we take a different approach and focus on extracting a single specified information from the build log as a whole with chunk retrieval techniques.
Chunk retrieval techniques are used as a part of log parsing to retrieve the values of variable parts in a log message, e.g.\ by using regular expressions~\cite{nagappan2010abstracting,xu2009detecting}.

@@

\section{Chunk Retrieval Techniques}
\label{sec:techniques}
This chapter introduces the concept of chunk retrieval techniques.
We use these techniques to extract text chunks from build logs that represent a specific, targeted information.
This chapter first presents how a build log, which we take as input to the chunk retrieval, is created by a continuous integration (CI) build.
Next, the chapter describes retrievable information chunks in build logs and gives examples found in Travis CI build logs.
We illustrate why it is useful to extract the presented information chunks.
The following section introduces our concept of chunk retrieval techniques.
We present the three chunk retrieval techniques we investigate in this paper:
program synthesis by example (PBE), common text similarity (CTS) and keyword search (KWS).

@@

\subsection{Characteristics of Chunk Retrieval Techniques}
\label{sec:blirt}
For this paper, we want to evaluate different techniques to retrieve information chunks from build logs, which we call \emph{chunk retrieval techniques}.
The techniques we investigate do not require to parse the structure of a whole build log, but focus on extracting just one specific information.

@@

@@

\noindent
\textbf{Configuration and Input}
Our study results show that chunk retrieval with PBE gives best results when the training examples are from one structural category.
This means it is suited to retrieve information chunks that always have the same surrounding structure.
To extract for example the reason a build failed, the log passage describing the failure would always have to be started and ended the same way.

@@

\noindent
\textbf{Retrieval Output Usage}
If the program synthesis succeeds and applying the regular expression program yields an output, PBE shows a high precision and a high recall.
The tool clearly identifies a failing program synthesis or when no output from the program applied to a build log is obtained.
Therefore, if there is an output, the user can have high confidence that it is the correct output.
This makes output from PBE chunk retrieval well suited for consumption by other software components.

\subsubsection{Common Text Similarity (CTS)}
\noindent
\textbf{Configuration and Input}
Chunk retrieval using CTS also yields better results the fewer structural categories are present in the training and test examples.

@@

\noindent
\textbf{Retrieval Output Usage}
CTS has good precision and recall on average, though the precision or recall of a chunk retrieval run is very hard to predict from the given result.
Therefore, retrieval output from CTS is suited to be read by a human.

\subsubsection{Keyword Search (KWS)}
\noindent
\textbf{Configuration and Input}
KWS has a higher recall than the two other techniques for multiple structural categories present in the training and test examples.
This makes KWS a good technique if there is little prior knowledge on how the targeted log chunk is represented in the build log to be analyzed.
For the example of extracting the reason the build failed, KWS is best suited if a build can fail in various steps logged by different tools and no pre-categorization of where the build failed is available.

@@

\noindent
\textbf{Retrieval Output Usage}
Even though KWS has the highest recall of all three techniques, its precision is also the lowest.
The output of a chunk retrieval with KWS is well suited to be read by humans.

@@

\noindent
\textbf{Caveat!} This is a preliminary theory based on the results from our comparison study.
The recommendations are therefore based on our implementation of the chunk retrieval techniques as well as the logs in the \emph{LogChunks} data set.

@@

\noindent
\textbf{Example of Using the Recommendation Scheme}
To illustrate how one would use our decision tree to find a suitable chunk retrieval technique we describe two concrete examples: a researcher investigating why CI builds fail and a software team wanting to monitor their build performance.

@@

\noindent
\textbf{Implementation}
Our results are highly dependent on our implementation of the investigated chunk retrieval techniques and the libraries we used.
Our implementation of PBE is severely based on the program synthesis provided by PROSE\@.
Its limitations are therefore also mainly influenced by this library.
For example, the need for examples from a single structural category stems from the fact that FlashExtract cannot learn regular expression programs with arbitrary boolean conjunctions and disjunctions~\cite{mayer2015user}.
This limitation was necessary to keep the synthesis performance reasonable.

@@

\noindent
\textbf{Data Set}
The outcomes of our comparison study are highly dependent on the build logs from the \emph{LogChunks} data set.
It only consists of build logs from open source projects and therefore it is not clear whether our results are generalizable to industry projects.
We only collected build logs from Travis CI, however we chose to evaluate on an information chunk whose format is not dependent on Travis CI\@.
This is because the reason the build failed is described within the build logs by the tools themselves and not the Travis CI environment.

\noindent
\textbf{Training Set Size}
Especially the results for CTS might be influenced by the fact that we only trained on one to five examples.
We chose this small training set size as the training examples have to be provided per repository and we expect a developer to not want to provide more examples than the small numbers we evaluated on.

\noindent
\textbf{Few Samples with Many Structural Categories}
Our comparison study shows fewer measurements with many structural categories than with one category.
This stems from the fact that we use a realistic data set which in many cases has only one or few structural categories.

\section{Conclusion and Future Work}
\label{sec:conclusion-fw}
The goal of this paper was to support researchers and developers in their decision on how to analyze build logs.
We implemented and compared three different chunk retrieval techniques on our data set \emph{LogChunks}, composed of 797 manually labeled build logs from a broad range of 80 repositories.
Our results show that the structural representation of the targeted information in the build logs is the main factor to consider when choosing a suitable technique.
Secondary factors are the desired confidence into recall and precision of the produced output and whether precision or recall is more important for the task at hand.

There are various future research opportunities based on our work:
\begin{itemize}
  \item \textbf{Further Analysis of \emph{LogChunks}} We created the \emph{LogChunks} data set specifically for our comparative study, though it can be the basis for various further analyses of build log data.
  The keywords, for example, can be investigated to answer which keywords are used to search for the reason the build failed within build logs.
  \item \textbf{Cross-Repository Build Log Analysis} We trained and tested each chunk retrieval technique on examples from the same repository.
  We propose to analyze how techniques could be trained across repositories, building the cornerstones for build environment-agnostic analysis tools.
  \item \textbf{Comparison with more Chunk Retrieval Techniques} This paper investigates the three chunk retrieval techniques PBE, CTS and KWS\@.
  Our study design can be reused to evaluate other build log analysis techniques, such as the diff and information retrieval approach by Amar et al.~\cite{amar2019mining}.
  \item \textbf{Refinement of Retrieval Quality for each Technique} We investigated basic configurations of existing techniques applied to chunk retrieval from build logs.
  In a next step, each of these techniques could be refined to better approach the domain of build logs.
  The \emph{LogChunks} data set and our study results act as a baseline to benchmark such technique improvements.
  We propose the following improvements:
    \begin{itemize}
      \item \textbf{Custom Ranking and Tokens for PBE} The program synthesis through PROSE ranks possible programs according to what the user most likely intended.
      One could adapt the ranking rules provided by the FlashExtract DSL to fit common build log chunk retrieval tasks.
      FlashExtract includes special tokens when enumerating possible regular expressions.
      One could extend these with tokens found in build logs, such as ``-'',``='',``ERROR'' or ``[OK''.
      \item \textbf{Meta-Parameter Optimization for CTS} Information retrieval techniques have various meta-parameters which can be optimized for the specific use case~\cite{panichella2016parameterizing}.
      We propose to further investigate improvements in preprocessing of the log text, in tokenization of the log lines into terms and in stop words lists.
    \end{itemize}
  \item \textbf{Usability Analysis of Chunk Retrieval Output} Our analysis of the output produced by the chunk retrieval focuses on precision and recall.
  We propose to investigate how useful these outputs are to developers through controlled experiments.
\end{itemize}
